Presentation Title

### 2017-08-18 thesis/chapters/ch1-intro.tex
Edit ch3

The primary innovation is the consensus mechanism which prevents double spending but also incentivises anyone (with adequate hardware) to participate and keep the network running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
If $C$ can simultaneously claim that she transferred 5 units to $A$ but also 5 units to $B$, then the system is inconsistent.
Bitcoin and many of its derivatives (e.g. Litecoin\footnote{\url{https://litecoin.org}} and Dogecoin\footnote{\url{http://dogecoin.org}}) solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is to reach agreement on a set of valid transactions. 
This effectively eliminates inconsistencies.

@@

\section{Contributions}
In this work, we take the advice of Croman et al.~\cite{croman2016scaling} and Vukoli\'{c}~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how value transfer work in the real world and how they work in early blockchain systems.
Take a restaurant owner, for example,
most of the time the customer is honest and pays the bill.
There is no need for the customer or the owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the owner would report the incident to some central authority, e.g. the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently leads to limited scalability because every transaction must be validated by the authority even when most of the transactions are legitimate.

>>>>

The primary innovation is the consensus mechanism which prevents double spending but also incentivises anyone (with adequate hardware) to participate and keep the network running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
If $C$ can simultaneously claim that she transferred 5 units to $A$ but also 5 units to $B$, then the system is inconsistent.
Bitcoin and many of its derivatives (e.g., Litecoin\footnote{\url{https://litecoin.org}} and Dogecoin\footnote{\url{http://dogecoin.org}}) solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is to reach agreement on a set of valid transactions. 
This effectively eliminates inconsistencies.

@@

\section{Contributions}
In this work, we take the advice of Croman et al.~\cite{croman2016scaling} and Vukoli\'{c}~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how value transfer work in the real world and how they work in early blockchain systems.
Take a restaurant owner, for example,
most of the time the customer is honest and pays the bill.
There is no need for the customer or the owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the owner would report the incident to some central authority, e.g., the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently leads to limited scalability because every transaction must be validated by the authority even when most of the transactions are legitimate.

### 2017-08-18 thesis/chapters/ch2-problem.tex
Edit ch3

This technique overcomes the early blockchain scalability issue by delegating the transaction validation to the Byzantine consensus protocol (e.g. PBFT in ByzCoin~\cite{kogias2016enhancing}).
A major tradeoff of such systems is that they cannot guarantee correctness when there is a large number of malicious nodes (but less than a majority).
For SCP, ByzCoin and Solidus, they all have some probability to elect more than $t$ Byzantine nodes into the committee,
where $t$ is typically just under a third of the committee size (a lower bound of Byzantine consensus~\cite{pease1980reaching}).
This problem is especially difficult to solve because the committee is always much smaller than the population size which has more than $t$ Byzantine nodes.
Classical blockchain does not have this problem because they do not use Byzantine consensus.
Further, due to the fact that these systems must reach consensus on all transactions, none of them achieves horizontal scalability.

% Our approach share many similarities with the hybrid systems.
% First, we also elect a committee (facilitators) to drive consensus.
% But we do not have proof-of-work for Sybil defence because we believe 
% it is possible to do it efficiently, e.g. using NetFlow~\cite{pimotte}.
% Secondly, our use of CP blocks and ACS is also unique.
% This creates a much higher throughput and enables censorship resiliance as mentioned earlier.
% For instance, ByzCoin performs just below 1000 TPS with a thousand nodes whereas we peak at 8000 TPS.

>>>>

This technique overcomes the early blockchain scalability issue by delegating the transaction validation to the Byzantine consensus protocol (e.g., PBFT in ByzCoin~\cite{kogias2016enhancing}).
A major tradeoff of such systems is that they cannot guarantee correctness when there is a large number of malicious nodes (but less than a majority).
For SCP, ByzCoin and Solidus, they all have some probability to elect more than $t$ Byzantine nodes into the committee,
where $t$ is typically just under a third of the committee size (a lower bound of Byzantine consensus~\cite{pease1980reaching}).
This problem is especially difficult to solve because the committee is always much smaller than the population size which has more than $t$ Byzantine nodes.
Classical blockchain does not have this problem because they do not use Byzantine consensus.
Further, due to the fact that these systems must reach consensus on all transactions, none of them achieves horizontal scalability.
